Reconstructing Propositional Proofs in Type Theory

### 2017-10-25 paper/main.tex
[ paper ] table added.
[ paper ] related work added.
[ paper ] removed HEAD.
[ paper ] last changes.
[ paper ] strip proof.
[ paper ] conjunct reviewed.
[ paper ] fixing lemmas.
[ paper ] working on resolve.
[ paper ] diagram fixed.
[ paper ] Eq removed.
[ paper ] lots of changes.
[ paper ] canon ==> simplify-and simplify-or.
[ paper ] reorder conclusions with future work.
[ bib ] Switched to biblatex.
[ bib ] Removed quotes from the titles.

\documentclass[
    envcountsect    %% In order to provide the usual behaviour expected
                    %% from \newtheorem
  , runningheads
  ]{llncs}

\spnewtheorem{mainth}[theorem]{Main Theorem}{\bfseries}{\rmfamily}

\usepackage[numbers]{natbib}

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ucs}
\usepackage{autofe}
\usepackage{afterpage}
\usepackage{comment}
\usepackage[hyphens]{url}
\usepackage{bm}

@@

\newenvironment{sketchproof}{%
  \renewcommand{\proofname}{Sketch of the Proof}\proof}{\endproof}
\renewcommand\qedsymbol{$\blacksquare$}

@@

\newunicodechar{¬}{\ensuremath{\neg}\;}
\newunicodechar{Γ}{\ensuremath{\Gamma}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{φ}{\ensuremath{\varphi}}
\newunicodechar{ψ}{\ensuremath{\psi}}
\newunicodechar{ϕ}{\ensuremath{\varphi}}
\newunicodechar{ᵢ}{\ensuremath{{}_{i}}}
\newunicodechar{₀}{\ensuremath{{}_{0}}}
\newunicodechar{₁}{\ensuremath{{}_{1}}}
\newunicodechar{₂}{\ensuremath{{}_{2}}}
\newunicodechar{₃}{\ensuremath{{}_{3}}}
\newunicodechar{₄}{\ensuremath{{}_{4}}}
\newunicodechar{₅}{\ensuremath{{}_{5}}}
\newunicodechar{₆}{\ensuremath{{}_{6}}}
\newunicodechar{₇}{\ensuremath{{}_{7}}}
\newunicodechar{₈}{\ensuremath{{}_{8}}}
\newunicodechar{₉}{\ensuremath{{}_{9}}}
\newunicodechar{ₙ}{\ensuremath{{}_{n}}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
\newunicodechar{∅}{\ensuremath{\emptyset}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{∧}{\ensuremath{\wedge}}
\newunicodechar{∨}{\ensuremath{\vee}}
\newunicodechar{∼}{\ensuremath{\sim}}
\newunicodechar{≠}{\ensuremath{\neq}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{⊕}{\ensuremath{\oplus}}
\newunicodechar{⊖}{\ensuremath{\ominus}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{⊤}{\ensuremath{\top}}
\newunicodechar{⊥}{\ensuremath{\bot}}
\newunicodechar{⊻}{\ensuremath{\veebar}}
\newunicodechar{⟝}{\ensuremath{\vdash_{2}}}
\newunicodechar{ⱼ}{\ensuremath{{}_{j}}}

@@

\newcommand{\fun}[1]{\rm{#1}\xspace}
\newcommand{\fbuild}{\fun{build}}
\newcommand{\fcanon}{\fun{canon}}
\newcommand{\fcnf}{\fun{cnf}}
\newcommand{\fdist}{\fun{dist}}
\newcommand{\ffactor}{\fun{factor}}
\newcommand{\fform}{\fun{form}}
\newcommand{\fmax}{\fun{max}}
\newcommand{\fndisj}{\fun{ndisj}}
\newcommand{\fnnf}{\fun{nnf}}
\newcommand{\frank}{\fun{rank}}
\newcommand{\frconj}{\fun{rconj}}
\newcommand{\frdisj}{\fun{rdisj}}
\newcommand{\freorder}{\fun{reorder}}
\newcommand{\frm}{\fun{rm}}
\newcommand{\fsbuild}{\fun{sbuild}}
\newcommand{\fsubst}{\fun{subst}}
\newcommand{\fuh}{\fun{uh}}
\newcommand{\tunshunt}{\fun{thm-uh}}

\newcommand{\fstrip}{\fun{strip}}
\newcommand{\tstrip}{\fun{thm-strip}}

@@

% latin etc. abbrev
\newcommand{\abbrev}[1]{#1} % alternative: \emph{#1}
\newcommand{\cf}{\abbrev{cf.}\ }
\newcommand{\eg}{\abbrev{e.\,g.}}
\newcommand{\Eg}{\abbrev{E.\,g.}}
\newcommand{\ie}{\abbrev{i.\,e.}}
\newcommand{\Ie}{\abbrev{I.\,e.}}
\newcommand{\etal}{\abbrev{et.\,al.}}
\newcommand{\wwlog}{w.\,l.\,o.\,g.} % \wlog is ``write into log file''
\newcommand{\Wlog}{W.\,l.\,o.\,g.}
\newcommand{\wrt}{w.\,r.\,t.}

@@

@@

\title{Proof-Reconstruction in Type Theory for Propositional Logic}
\author{Jonathan Prieto-Cubides%
%\and Andr\'es Sicard-Ram\'irez
}
%

@@

\subfile{sections/abstract.tex}
% \tableofcontents
\subfile{sections/introduction.tex}
% \subfile{sections/preliminaries.tex}
\subfile{sections/metis-language-and-proofs.tex}
\subfile{sections/proof-reconstruction.tex}
% \subfile{sections/implementation.tex}
\subfile{sections/related-work.tex}
\subfile{sections/conclusions.tex}
\subfile{sections/acknowledgements.tex}

\bibliographystyle{plainnat}
\bibliography{ref}
\addcontentsline{toc}{section}{References}

\newpage
\subfile{sections/appendices.tex}

>>>>

\documentclass[
    envcountsect    %% In order to provide the usual behaviour expected
                    %% from \newtheorem
  , runningheads
  % , fleqn           %% all equations in the document left aligned
  ]{llncs}

% \setlength{\mathindent}{1cm}

\spnewtheorem{mainth}{Theorem}[section]{\bfseries}{\rmfamily}
\spnewtheorem{mainlemma}{Lemma}[section]{\bfseries}{\rmfamily}
\spnewtheorem*{notation}{Notation}{\it}{\rmfamily}
\spnewtheorem*{myremark}{Remark}{\it}{\rmfamily}
\spnewtheorem*{myexample}{Example}{\it}{\rmfamily}

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{autofe}
\usepackage{afterpage}
\usepackage{comment}
\usepackage[hyphens]{url}
\usepackage{bm}

@@

\newenvironment{sketchproof}{%
  \renewcommand{\proofname}{Sketch of the Proof}\proof}{\endproof}

\renewcommand\qedsymbol{$\blacksquare$}

@@

\newunicodechar{¬}{\ensuremath{\neg}\;}
\newunicodechar{Γ}{\ensuremath{\Gamma}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{φ}{\ensuremath{\varphi}}
\newunicodechar{ψ}{\ensuremath{\psi}}
\newunicodechar{ϕ}{\ensuremath{\varphi}}
\newunicodechar{ᵢ}{\ensuremath{{}_{i}}}
\newunicodechar{₀}{\ensuremath{{}_{0}}}
\newunicodechar{₁}{\ensuremath{{}_{1}}}
\newunicodechar{₂}{\ensuremath{{}_{2}}}
\newunicodechar{₃}{\ensuremath{{}_{3}}}
\newunicodechar{₄}{\ensuremath{{}_{4}}}
\newunicodechar{₅}{\ensuremath{{}_{5}}}
\newunicodechar{₆}{\ensuremath{{}_{6}}}
\newunicodechar{₇}{\ensuremath{{}_{7}}}
\newunicodechar{₈}{\ensuremath{{}_{8}}}
\newunicodechar{₉}{\ensuremath{{}_{9}}}
\newunicodechar{ₙ}{\ensuremath{{}_{n}}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
\newunicodechar{∅}{\ensuremath{\emptyset}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{∧}{\ensuremath{\wedge}}
\newunicodechar{∨}{\ensuremath{\vee}}
\newunicodechar{∼}{\ensuremath{\sim}}
\newunicodechar{≠}{\ensuremath{\neq}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{⊕}{\ensuremath{\oplus}}
\newunicodechar{⊖}{\ensuremath{\ominus}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{⊤}{\ensuremath{\top}}
\newunicodechar{⊥}{\ensuremath{\bot}}
\newunicodechar{⬓}{\ensuremath{\square}}
\newunicodechar{⊻}{\ensuremath{\veebar}}
\newunicodechar{⟝}{\ensuremath{\vdash_{2}}}
\newunicodechar{ⱼ}{\ensuremath{{}_{j}}}

@@

\newcommand{\fun}[1]{\rm{#1}\xspace}
\newcommand{\fassoc}{\fun{assoc}}
\newcommand{\fbuild}{\fun{build}}
\newcommand{\fcanon}{\fun{simplify}}
\newcommand{\fcnf}{\fun{cnf}}
\newcommand{\fdist}{\fun{dist}}
\newcommand{\ffactor}{\fun{factor}}
\newcommand{\fform}{\fun{form}}
\newcommand{\fmax}{\fun{max}}
\newcommand{\fndisj}{\fun{ndisj}}
\newcommand{\fnnfp}{\fun{nnf}₀}
\newcommand{\fnnf}{\fun{nnf}}
\newcommand{\fpolarity}{\fun{polarity}}
\newcommand{\frank}{\fun{rank}}
\newcommand{\frconj}{\fun{rconj}}
\newcommand{\frdisj}{\fun{rdisj}}
\newcommand{\freorder}{\fun{reorder}}
\newcommand{\frm}{\fun{rm}}
\newcommand{\fsbuild}{\fun{sbuild}}
\newcommand{\fstripp}{\fun{strip}\prime}
\newcommand{\fstrip}{\fun{strip}}
\newcommand{\fsubst}{\fun{subst}}
\newcommand{\fuh}{\fun{uh}}
\newcommand{\tunshunt}{\fun{thm-uh}}

@@

% latin etc. abbrev
\newcommand{\abbrev}[1]{#1} % alternative: \emph{#1}
\newcommand{\cf}{\abbrev{cf.}\ }
\newcommand{\eg}{\abbrev{e.\,g.}}
\newcommand{\Eg}{\abbrev{E.\,g.}}
\newcommand{\ie}{\abbrev{i.\,e.}}
\newcommand{\Ie}{\abbrev{I.\,e.}}
\newcommand{\etal}{\abbrev{et.\,al.}}
\newcommand{\wwlog}{w.\,l.\,o.\,g.} % \wlog is ``write into log file''
\newcommand{\Wlog}{W.\,l.\,o.\,g.}
\newcommand{\wrt}{w.\,r.\,t.}
\newcommand{\TheEnd}{\\\hspace*{0.975\textwidth}$\blacksquare$}

@@

% -------------------------------------------------------------------
% biblatex.
% -------------------------------------------------------------------

\usepackage[%
backend=biber,
% bibstyle=authoryear,%
% citestyle=authoryear-comp,%
% giveninits=false,%%
% maxcitenames=4,%
]{biblatex}
\usepackage{csquotes}

\addbibresource{ref.bib}

% Remove the quotes from the title.
\DeclareFieldFormat
  [article,%
  incollection,%
  inproceedings,%
  thesis,% works for mastersthesis and phdthesis
  unpublished,%
  ]{title}{#1}

@@

\title{Reconstructing Propositional Proofs in Type Theory}
% \title{Proof-Reconstruction in Type Theory for Propositional Logic}
\author{Jonathan Prieto-Cubides%
%\and Andr\'es Sicard-Ram\'irez
}
%

@@

\subfile{sections/abstract.tex}
% \tableofcontents
\subfile{sections/introduction.tex}
\subfile{sections/limitations-type-theory.tex}
\subfile{sections/metis-language-and-proofs.tex}
\subfile{sections/proof-reconstruction.tex}
% \subfile{sections/implementation.tex}
\subfile{sections/related-work.tex}
\subfile{sections/conclusions-and-future-work.tex}
\subfile{sections/acknowledgements.tex}

\printbibliography
\addcontentsline{toc}{section}{References}

% \newpage
% \subfile{sections/appendices.tex}
